---
title: "Jr3869_hw9"
author: "Jingwei Ren"
date: "11/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(modelr)
library(leaps)
```

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric.


```{r}
homicide= read_csv('./data/homicide-data.csv') 
homicide = homicide %>%  
  mutate(city_state = str_c(city, ",", state),
         case_status = ifelse(disposition == "Closed by arrest", 1, 0)) %>% 
  filter(!(city_state %in% c('Dallas,TX', 'Phoenix,AZ','Kansas City,MO',"Tulsa,AL"))) %>%
  mutate(victim_race = ifelse(victim_race == "White", "White", "Nonwhite"), victim_race = factor(victim_race, levels = c("White", "Nonwhite")),
victim_age = as.numeric(victim_age))
```


For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.


```{r}


```