---
title: "Jr3869_hw9"
author: "Jingwei Ren"
date: "11/26/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(modelr)
library(leaps)
```

Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. Omit cities Dallas, TX; Phoenix, AZ; and Kansas City, MO – these don’t report victim race. Also omit Tulsa, AL – this is a data entry mistake. Modifiy victim_race to have categories white and non-white, with white as the reference category. Be sure that victim_age is numeric.


```{r}
homicide= read_csv("./data/homicide-data.csv") 

homicide_tidy= homicide %>% 
  mutate(city_state = str_c(city, state, sep = ", "),
         homi_status = as.numeric(disposition == "Closed by arrest")) %>% 
  filter(!city_state %in% c("Dallas, TX","Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>%
  mutate(victim_race = fct_relevel(ifelse(victim_race == "White", "white", "non-white"), "white"),
victim_age = as.numeric(victim_age))
```


For the city of Baltimore, MD, use the glm function to fit a logistic regression with resolved vs unresolved as the outcome and victim age, sex and race (as just defined) as predictors. Save the output of glm as an R object; apply the broom::tidy to this object; and obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing non-white victims to white victims keeping all other variables fixed.


```{r}
baltimore = homicide_tidy %>% 
  filter(city_state == "Baltimore, MD")

logistic = 
  baltimore %>% 
  stats::glm(homi_status ~ victim_age + victim_sex + victim_race, data = ., family = binomial())

logistic %>% 
  broom::tidy() %>%  # give log odds ratio
  mutate(OR = exp(estimate), # transform back
         conf.low = exp(estimate - std.error*1.96),
         conf.high = exp(estimate + std.error*1.96)) %>%
  select(term, log_OR = estimate, OR, conf.low, conf.high) %>% 
  filter(term == "victim_raceNonwhite") %>%
  knitr::kable(digits = 3)

```
The result of logistic model showed that the estimate of the adjusted odds ratio is 0.441, with confidence interval from (0.31, 0.62)


Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing non-white victims to white victims. Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.


```{r}
each_city = homicide_tidy %>% 
  group_by(city_state) %>% 
  nest()
OR_summary = each_city %>% 
  mutate(models = map(data, ~ stats::glm(homi_status ~ victim_age + victim_sex + victim_race, data = .x, family = binomial())),
    models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest() %>% 
  filter(term == "victim_racenon-white") %>% 
  mutate(OR = exp(estimate),
         conf.low = exp(estimate - std.error*1.96),
         conf.high= exp(estimate + std.error*1.96)) %>%
  select(city_state, term, log_OR = estimate, OR, conf.low, conf.high) 
```
Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.


```{r}
OR_summary %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + geom_point() + 
  geom_errorbar(mapping = aes(ymin = conf.low, ymax = conf.high)) +
  theme_bw() +
  theme(legend.position = "bottom",
        legend.direction = "horizontal",
        axis.text.x = element_text(angle = 90, size = 6))+
  labs(title = "Estimate and 95% CI of solving homicides odds ratio for each city", 
         x = "City and State", 
         y = "OR") 

```

Based on the plot, the estimate odds ratio of solving homicides comparing non-white vitctims to white victims varies cross different states and cities. The estimates are mostly lower than one, which menas that homicides in which the victim is non-white are less likely to be resolved compared to those in which the victim is white. 

